### 2015-03-14 technique.tex
fix in the text

Figure~\ref{fig:whoop} depicts the \whoop infrastructure. Initially, \whoop accepts a kernel module written in C, together with a Linux environmental model. The environmental model (i.e. stub Linux header files) is required to ``close'' the module and allow it to be translated and subsequently analysed. Both the module and the environmental model are passed to the translation phase of \whoop (see Section~\ref{tech:translation}), which outputs an over-approximated program written in the Boogie intermediate verification language (IVL)~\cite{deline2005boogiepl}. Next, the analysis phase of \whoop runs (see Section~\ref{tech:analysis}), detecting all potential data races in the abstract program. Finally, \whoop uses information from the race analysis phase to accelerate bug finding with \corral (see Section~\ref{tech:bugfinding}).

>>>>

Figure~\ref{fig:whoop} depicts the \whoop infrastructure. Initially, \whoop accepts a kernel module written in C, together with a Linux environmental model. The environmental model (i.e. stub Linux header files) is required to ``close'' the module and allow it to be translated and subsequently analysed. Both the module and the environmental model are passed to the translation phase of \whoop (see Section~\ref{tech:translation}), which outputs an over-approximated program written in the Boogie intermediate verification language (IVL)~\cite{deline2005boogiepl}. Next, \whoop performs its static lockset analysis (see Section~\ref{tech:analysis}) to detect all potential data races in the abstract program. Finally, \whoop uses information from the static analysis phase to accelerate bug finding with \corral (see Section~\ref{tech:bugfinding}).
